### 2025-06-22 modern-portfolio-theory.qmd
20250621 - reorder
20250621 - fold code

```{r}
hiLo_permutations <- expand.grid(
  rep(list(c("Hi", "Lo")), 3),
  stringsAsFactors = FALSE
)

@@

```{r}
qbRbWr_projections2 <- data.frame(
  condition = c("Hi", "Lo"),
  qb_name = c("Josh Allen", "Patrick Mahomes"),
  rb_name = c("Saquon Barkley", "David Montgomery"),
  wr_name = c("Ja'Marr Chase", "Stefon Diggs")
)

>>>>

```{r}
#| code-fold: true

hiLo_permutations <- expand.grid(
  rep(list(c("Hi", "Lo")), 3),
  stringsAsFactors = FALSE
)

@@

```{r}
#| code-fold: true

qbRbWr_projections2 <- data.frame(
  condition = c("Hi", "Lo"),
  qb_name = c("Josh Allen", "Patrick Mahomes"),
  rb_name = c("Saquon Barkley", "David Montgomery"),
  wr_name = c("Ja'Marr Chase", "Stefon Diggs")
)
